---
title: "Untitled"
output: ioslides_presentation
date: "2023-10-04"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}

library(wordcloud)
library(wordcloud2)
library(tm)
library(magrittr)
library(readxl)
library(readr)
library(shiny)

kp <- read_excel("gsoko.xlsx")



text <- kp$Commodity
# Create a corpus  
docs <- Corpus(VectorSource(text))

docs <- docs %>%
  tm_map(removeNumbers)%>%
  tm_map(removePunctuation)%>%
  tm_map(stripWhitespace)
  

docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))

dtm <- TermDocumentMatrix(docs) 
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 34)


matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)
dtm
words
df

set.seed(1234) # for reproducibility 

wordcloud(words = df$word, freq = df$freq, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35,colors=brewer.pal(8, "Dark2"))

wordcloud2(data=df, size=1.6, color='random-dark')

#renderPlot({
#    wordcloud2(data=df, size=1.6, color='random-dark')
#  })


```

